### 2023-02-28 notebooks/conformal.qmd
confused about domain of classification loss

```{julia}
using CCE
using ConformalPrediction
using CounterfactualExplanations
using CounterfactualExplanations.Data
using CounterfactualExplanations.Objectives
using Flux
using MLJBase
using MLJFlux
using Plots
```

@@

```{julia}
#| output: true
#| echo: false
#| label: fig-losses
#| fig-cap: "Illustration of the smooth size loss and the configurable classification loss."

p1 = contourf(mach.model, mach.fitresult, X, y; plot_set_loss=true, zoom=0)
p2 = contourf(mach.model, mach.fitresult, X, y; plot_classification_loss=true, target=target, zoom=0)
plot(p1, p2, size=(800,320))
```

@@

# Generators:
generators = Dict(
    ordered_names[1] => GenericGenerator(opt = opt, decision_threshold=0.5),
    ordered_names[2] => GenericGenerator(opt = opt, decision_threshold=0.9),
    ordered_names[3] => CCE.ConformalGenerator(opt=opt, λ=[0.1,1]),
    ordered_names[4] => CCE.ConformalGenerator(opt=opt, λ=[0.1,10]),
)

>>>>

```{julia}
using CCE
using ConformalPrediction
using CounterfactualExplanations
using CounterfactualExplanations.Data
using CounterfactualExplanations.Objectives
using Flux
using LinearAlgebra
using MLJBase
using MLJFlux
using Plots
```

@@

```{julia}
#| output: true
#| echo: false
#| label: fig-losses
#| fig-cap: "Illustration of the smooth size loss and the configurable classification loss."
temp = 0.5
p1 = contourf(mach.model, mach.fitresult, X, y; plot_set_loss=true, zoom=0, temp=temp)
p2 = contourf(mach.model, mach.fitresult, X, y; plot_classification_loss=true, target=target, zoom=0, temp=temp, clim=nothing, loss_matrix=ones(2,2))
plot(p1, p2, size=(800,320))
```

@@

opt = Descent(0.01)
temp = 0.75
ordered_names = [
    "Generic (γ=0.5)",
    "Generic (γ=0.9)",
    "Conformal (λ₂=1)",
    "Conformal (λ₂=10)"
]
loss_fun = Objectives.logitbinarycrossentropy

# Generators:
generators = Dict(
    ordered_names[1] => GenericGenerator(opt = opt, decision_threshold=0.5),
    ordered_names[2] => GenericGenerator(opt = opt, decision_threshold=0.9),
    ordered_names[3] => CCE.ConformalGenerator(opt=opt, λ=[0.1,1], temp=temp),
    ordered_names[4] => CCE.ConformalGenerator(opt=opt, λ=[0.1,10], temp=temp),
)
